\section*{Abstract}
\label{sec:abstract}

The Oak Ridge Leadership Computing Facility (OLCF) is a leader in large-scale
parallel file system development, design, deployment and continuous operation.
For the last decade, the OLCF has designed and deployed two large center-wide
parallel file systems. The first instantiation, Spider 1, served the Jaguar 
supercomputer and its predecessor, Spider 2, now serves the Titan supercomputer, 
among many other OLCF computational resources. The OLCF has been rigorously 
collecting file and storage system statistics from these Spider systems since their
transition to production state.

In this paper we present the collected I/O workload statistics from the Spider
2 system and compare it to the Spider 1 data. Our analysis show that the Spider 2
workload is more more write-heavy I/O compared to Spider 1 (75\%
vs. 60\%, respectively). The data also show the OLCF storage policies
such as periodic purges are effectively managing the capacity resource of
Spider 2.  Furthermore, due to improvements in tdm\_multipath and ib\_srp
software, we are utilizing the Spider 2 system bandwidth and latency resources
more effectively.  The Spider 2 bandwidth usage statistics shows that our
system is working within the design specifications. However, it is also evident
that our scientific applications can be more effectively served by a burst
buffer storage layer.  All the data has been collected by monitoring tools
developed for the Spider ecosystem. We believe the observed data set and
insights will help us better design the next-generation Spider file and storage
system. It will also be helpful to the larger community for building more
effective large-scale file and storage systems.

 
